Classifier

### 2019-03-01 Code/01_build_classification_model.Rmd
Added more info to the 01 file.

# Execute Code
To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it. In our case, we want to store the model in Output/models and name the model class_mod_1.dat. Within R, we'll refer to this file path as file_model.

As a data input for training our model, we already have two text files: train_data_1.txt and test_data_1.txt. The file paths to these text files (already built) will be referred to as train_data and test_data.
```{r}
file_model <- "Output/models/class_mod_1.dat"
train_data <- "Output/clean_data/train_data_1.txt"
test_data <- "Output/clean_data/test_data_1.txt"
```

## Clean Data

## Build Model

>>>>

# Execute Code

## List File Paths of Model and Data
To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it. In our case, we want to store the model in Output/models and name the model class_mod_1.dat. Within R, we'll refer to this file path as file_model.

As a data input for training our model, we already have two text files: train_data_1.txt and test_data_1.txt. The file paths to these text files (already built) will be referred to as train_data and test_data.

```{r}
file_model <- "Output/models/class_mod_1.dat"
train_data_path <- "Output/clean_data/train_data_1.txt"
test_data_path <- "Output/clean_data/test_data_1.txt"
```

## Read in the Data
We have our training and test data kept in one csv file. We'll read it in after we've filtered all short tweets (with greater than five characters). We'll name this object tweet_data.
```{r}
# This code (and all code below) is broken because we don't have access to a tweet_sample_5k_full.csv file.

# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>%  
#  filter(nchar(tweet_text) > 5)
```

## Format the Training Data
For any supervised learning model (such as complaint classification), our training and test datasets need to have data labeled with the "correct" answers. This will allow our model to "learn" the correct answers, and it will hopefully help our model accurately predict correct answers.

For our fastText model, we need to make sure each tweet is preceded by a label (in our case, the labels will be "complaint" and "non-complaint". fastText labels have two underscores before and after the label. For example, our complaint labels need to look like this: __label__complaint. Furthermore, the data we feed into the fastText model needs to be a character vector (like a .txt file), not a dataframe. We'll have to do some formatting before we get to that point.

Now that we have access to the data, we'll edit a variable named "label." Currently the labels are 0 for non-complaints and 1 for complaints. When we're done, we'll replace the 0's and 1's with their respective terms. Additionally, the label and text need to be in the same cell, so we'll make a new variable that concotenates the text and the label toghether.

Finally, we need to randomly and evenly tag our data: half of it will become training, and half of it will become test data.

```{r}
# test_train_data <- 
#   tweet_data %>% 
#   mutate(label = case_when(label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
#                               label == 1 ~ "complaint"),
#             input_lines = paste(label, tweet_text)) %>% 
#   group_by(label) %>% # get a representative sample of both complaints and non complaints
#   mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
#   ungroup()
```

### Create the .txt Files
As mentioned earlier, we need to create a text file of our training and test datasets because the fastText model only takes character vectors as inputs. With our data labeled both for training/test and complaint/non-complaint, we're ready to do this. We will use the write_lines() function to do this. The train_data_path is the file location we specified earlier in this script.

!!!!!!!!!! I'm still not sure how we are using the test_labels_without_prefix. If its not the test data, what is it?

```{r}
# write train data
# train_data_lines <- 
#   test_train_data %>% 
#   filter(test_train == "train") %>% 
#   pull(input_lines) %>% 
#   paste0("__label__", .)
# 
# write_lines(train_data_lines, train_data_path)
# 
# # write test data
# test_data_lines <- 
#   test_train_data %>% 
#   filter(test_train == "test") %>% 
#   pull(input_lines) %>% 
#   paste0("__label__", .)
# 
# write_lines(test_data_lines, test_data_path)

# create a character vector containing the tweets to test without their labels
test_labels_without_prefix <- 
  test_train_data %>% 
  filter(test_train == "test") %>% 
  pull(label)
```

## Train the Model
The package we are using (fastrtext) uses the execute() function to train the model. This function makes more sense if you've followed the fastText tutorials, but put simply, it concotenates the arguments into a single command which is then run in the terminal.

After we train the model, we'll load the model into our environment.

"supervised" specifies that this is a supervised model (classification, as opposed to creating word vectors). 
"-input" specifies the file location of the training text files.
"-output" specifies the file location where we want to place our model, once it has finished training.

You can find more information about the parameters of the model (such as -dim, -lr, and -epoch) here: https://fasttext.cc/docs/en/options.html.

!!!!!! Considering that this is such a large dataset, it might be worthwhile to use -loss hs (hierarchical softmax) to speed up the training. It should not significantly affect accuracy.

```{r}
# train model
execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))

# load model
model <- load_model(file_model)
```

## Review Model:
We'll want to see how a few of the predictions turned out. 
```{r}
# prediction are returned as a list with words and probabilities
predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
head(predictions, 5)
```

This will help us confirm that our model worked as expected.
```{r}
length(predictions)
length(test_labels_without_prefix)
length(test_data_lines)
```

## Accuracy
Let's look at how accurately the model predicted names
```{r}
# Compute accuracy
mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
```

Here, we'll look at the hamming loss, and a few of the predictions.

The hamming loss is the number of wrong labels over the total number of labels. Hamming loss is most useful when applied to multi-classifiers because when it is done with binary classifiers (such as ours), it is simply equal to 1 - accuracy.
```{r}
# because there is only one category by observation, hamming loss will be the same
get_hamming_loss(as.list(test_labels_without_prefix), predictions)

# test predictions
predictions <- predict(model, sentences = test_to_write)
print(head(predictions, 5))

# you can get flat list of results when you are retrieving only one label per observation
print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
```
